\section{Introduction to the Riemann Zeta Function}
We give a quick introduction to the Zeta function in this section, including its product representation and analytic continuation.
\begin{definition}[Zeta Function]
	Let $s\in\complex$ with $\Re(s)>1$. Then \begin{equation}
	\zeta(s)=\sum_{n=1}^{\infty}\frac{1}{n^s}.
	\end{equation}
\end{definition}
The zeta function converges absolutely on $\Re(s)>1$ by comparing to the integral $\int x^{-\Re(s)} dx$.
The properties of the zeta function as they relate to the distribution primes. In particular, the Dirichlet series can be represented as a product of primes.
\begin{proposition}\label{eulerproduct}
	On $\Re(s)>1$, \begin{equation}
		\zeta(s) = \prod_{p\in\mathbb{N}}\left(1-\frac{1}{p^s}\right)^{-1}.	
	\end{equation}
\end{proposition}
\begin{remark}
	This expresion also converges absolutely for $\Re(s)>1$. Since \[
		\left(1-\frac{1}{p^s}\right)^{-1} = \frac{p^s}{p^s-1} = 1 + \frac{1}{p^s-1}
	\]
	and $\sum(p^s-1)^{-1}$ converges absolutely by comparison to the zeta function Dirichlet series.
\end{remark}
\begin{proof}[Sketch of proof]
	Write $s=\sigma+it$. For each $p$,\[
		\left(1-\frac{1}{p^s}\right)^{-1} = \left(\frac{1}{p^s}+\frac{1}{p^{2s}}+\frac{1}{p^{3s}}+...\right)
	\]
	converges absolutely for $\Re(s)>1$ and uniformly across all $p$. We thus take for $m>N$ \begin{align*}
		\prod_{p\leq N}\left(1-\frac{1}{p^s}\right)^{-1}  &= \prod_{p\leq N}\left(\sum_{k=1}^{m} \frac{1}{p^{ks}}+O(2^{-m\sigma})\right)\\
		&\stackeq{(*)}\sum_{n=1}^{N}\frac{1}{n^s}+O(\sum_{n=N+1}^{\infty} \frac{1}{n^\sigma}) + O(2^{-m\sigma})\\
		&=\zeta(s) + O(\sum_{n=N+1}^{\infty} \frac{1}{n^\sigma}) + O(2^{-m\sigma})
	\end{align*}
	Where we apply to Fundemental Theorem of Arithmetic in (*) to show that each term $n^{-s}$ has coefficient $1$ determined by the unique prime factorization.
	As $m\to\infty$, $2^{-m\sigma} \to 0$. Then we take $N\to\infty$, the tail of the infinite sum converges to zero too.
\end{proof}
\begin{proposition} \label{analyticcontinuation}
	$\zeta$ extends to a meromorphic function on $\complex$ with a simple pole at $s=1$. By abuse of notation, we identify the extension of the zeta function with $\zeta$ too.
\end{proposition}

We will prove Proposition \ref{analyticcontinuation} in two steps. First, we will extend $\zeta$ to $\sigma>0$. Then, we will describe the continuation of the zeta function to the whole plane using by its functional equation: $\zeta$ has a line of symmetry across $\Re (s)=1/2$.
\begin{proposition}\label{extension}
	Let $\xi(s)\defeq \pi^{-s/2}\Gamma(s/2)\zeta(s)$. Then \begin{equation}\label{symmetryeq}
		\xi(s) = \xi(1-s).
	\end{equation}
\end{proposition}
\begin{proof}[Extension of $\zeta$ to $\sigma>0$]
	We apply integration by parts on Dirichlet series when $\sigma>1$ \begin{align*}
		\zeta(s)&=\int_{1/2}^{\infty} x^{-s} d \lfloor x \rfloor \\
				&= s \int_{1/2}^{\infty} \lfloor x \rfloor x^{-s-1} d x\\
				&=  s \int_{1}^{\infty}  x^{-s} - \frac{\{x\}}{x^{-s-1}} d x\\
				&= \frac{s}{s-1} - s \int_{1}^{\infty} \frac{\{x\}}{x^{-s-1}} dx\\
	\end{align*}
	where in the last expression, the integral converges when $\sigma>0$, and the pole at $s=1$ arises from the first term.
\end{proof}


\begin{proof}[Proof of Proposition \ref{extension}]
	Using \begin{align*}
		\Gamma(s)=\int_{0}^{\infty} e^{-x}x^{s-1}dx,
	\end{align*}
	we make the substitution $x=\pi n^2y$ to get \begin{align*}
		\Gamma(s)&= \int_{0}^{\infty} e^{-\pi n^2 y} (\pi n^2 y)^{s-1} \pi n^2 dy\\
		\implies \frac{\Gamma(s)}{\pi^s n^{2s}} &= \int_{0}^{\infty} e^{-\pi n^2 y} y^{s-1} dy
	\end{align*}
	So that by the Monotone Convergence Theorem,\begin{align*}
		\pi^{-s/2}\Gamma(s/2)\zeta(s) &= \sum_{n=1}^{\infty}\frac{\Gamma(s/2)}{\pi^{s/2} n^s}\\
		&= \sum_{n=1}^{\infty} \int_{0}^{\infty} e^{-\pi n^2x} x^{s/2-1} dx\\
		&=  \int_{0}^{\infty}\sum_{n=1}^{\infty}\left(e^{-\pi n^2 x}\right)  x^{s/2-1} dx.
	\end{align*}
	We now let \[
		\omega(x) = \sum_{n=1}^{\infty} e^{-\pi n^2 x}, \quad \theta(x) = \sum_{n=-\infty}^{\infty} e^{-\pi n^2 x} = 2\omega(x)+1,
	\]
	and apply Poisson Summation to \begin{align*}
		\theta(x) &= \sum_{n=-\infty}^{\infty} e^{-\pi n^2 x}\\
		&= \sum_{k=-\infty}^{\infty} \int_{-\infty}^{\infty} e^{-\pi y^2 x} e^{-2\pi i k y} dy\\
		&= \sum_{k=-\infty}^{\infty} \int_{-\infty}^{\infty} e^{-\pi y^2 x} e^{-2\pi i k y} dy\\
		&= \sum_{k=-\infty}^{\infty} \frac{1}{\sqrt{x}} \int_{-\infty}^{\infty} e^{-\pi u^2} e^{-2\pi i k u /\sqrt{x}} du\\
		&= \sum_{k=-\infty}^{\infty} \frac{1}{\sqrt{x}} e^{-\pi k^2  / x}\\
		&= \frac{1}{\sqrt{x}} \theta \left(\frac{1}{x}\right)
	\end{align*}
	using the substitution $y\sqrt{x}=u$. Replacing with $\omega$, \[
	\sqrt{x}(2\omega(x)+1) = 2\omega\left(\frac{1}{x}\right)+1
	\implies \omega\left(\frac{1}{x}\right)=\sqrt{x}\omega(x) +\frac{\sqrt{x}}{2} - \frac{1}{2}.
	\]
	We thus write, using $y=1/x$, \begin{align*}
		\xi(s) &= \int_{0}^{1}\omega(x) x^{s/2-1} dx +
		\int_{1}^{\infty}\omega(x)  x^{s/2-1} dx\\
		&=\int_{1}^{\infty}\omega(1/y) y^{-s/2-1} dy +
		\int_{1}^{\infty}\omega(x)  x^{s/2-1} dx\\
		&=\int_{1}^{\infty}\left(
		\sqrt{y}\omega(y) +\frac{\sqrt{y}}{2} - \frac{1}{2}
		\right) y^{-s/2-1} dy +
		\int_{1}^{\infty}\omega(x)  x^{s/2-1} dx\\
		&= \int_{1}^{\infty}\left(
			\frac{\sqrt{y}}{2} - \frac{1}{2}
			\right) y^{-s/2-1} dy+ \int_{1}^{\infty}\omega(x)  \left(x^{s/2-1} + x^{-s/2-1/2}\right)dx\\
		&= \frac{1}{1-s} + \frac{1}{s}+  \int_{1}^{\infty}\omega(x)  \left(x^{s/2-1} + x^{-s/2-1/2}\right)dx\\
		&= \frac{1}{s(1-s)}+ \int_{1}^{\infty}\omega(x)  \left(x^{s/2-1} + x^{-s/2-1/2}\right)dx.
	\end{align*}
	$\omega$ decays exponentially in $x$, so the integral converges and the last expression is well defined on $\complex$ with simple poles at $s=1$ or $s=0$.
	Finally, notice that the last expression is symmetric when $s$ is replaced with $(1-s)$, so proves equation \ref{symmetryeq}.
\end{proof}
Finally, we extend to $\zeta(0)$ by noticing that the poles of the functional equation from $\zeta(1)$ and $\Gamma(0)$ cancel out, so the Riemann Extension Theorem can be applied.

From the functional equation, we get `trivial' zeros of the zeta function from the poles of $\Gamma$. 

\begin{corollary}
	On $\Re(s)>1$ or $\Re(s)<0$, $\zeta(s)\neq 0$, except $\forall n\in\naturals, \zeta(-2n)=0.$
\end{corollary}
\begin{proof}
	Using the product representation of $\zeta$ where it converges, none of $(1-p^{-s})^{-1} =0$, so $\zeta(s)\neq 0$ on $\Re(s)>1$.
	$\Gamma$ has no zeros and has a simple pole at $-n$ for all $n\in\naturals$, so by equation \ref{symmetryeq} we get the zeros for $\Re(s)>0$ are exactly at the negative even integers.
\end{proof}
These zeros are known as the trivial zeros of $\zeta$. The remaining zeros lie between $0\leq \Re(s) \leq 1$.
\begin{definition}[Critical Strip and Critical Line]
	We denote the region $0\leq \Re(s) \leq 1$ as the \textbf{critical strip}. We denote the line $\Re(s) = 1/2$ as the \textbf{critical line}.
\end{definition}

\begin{corollary}
	On the critical strip, if $\zeta(s)=0$, $\zeta(\overline{s})=\zeta(1-s)=\zeta(1-\overline{s})=0.$
\end{corollary}
\begin{proof}
	This follows from equation \ref{symmetryeq}, and $\zeta(\overline{s})=\overline{\zeta(s)}$ holds where the Dirichlet series converges, thus holds everywhere.
\end{proof}
The number of zeros in the critical strip can be calculated using the argument principle applied to the function $\xi$ over the box with corners $-1+iT$,$-1-iT$,$2-iT$,$2+iT$.
Applying the functional equation, we get the following result.

\begin{theorem}[Number of zeros of $\zeta$] \label{numberzero}
	The number of zeros up to height $T$\[
	\#\{\sigma+it \ | \ \zeta(\sigma+it)=0,0 \leq \sigma\leq 1, |t|\leq T \} = \frac{T}{2\pi}\log{\frac{T}{2\pi e}} + O(\log T).
	\]
\end{theorem}
Theorem \ref{numberzero} is obtained by Riemann in his famous 1859 paper on the Zeta function, where he analytically continued the Zeta function and conjectured that all the zeros lie on the critical line \cite{Riemann1859}.
\begin{conjecture}[Riemann Hypothesis] \label{RH}
	The \textbf{Riemann Hypothesis} (RH) asserts that on the critical strip, \[
	\zeta(s) = 0 \implies \Re(s) = \frac{1}{2}. 
	\]
\end{conjecture}
